\chapter{Introduction}
\label{ch:Introduction}

Reducing code complexity is a crucial measure in software projects to counteract rising costs for development and maintenance. Nowadays, many applications make use of external components instead of being built completely from scratch. Software reuse increases the productivity of the developers and improves the overall quality of the resulting product. These benefits encourage the popularity of third-party libraries which provide an interface to pretested features, created and maintained by a different team. This public interface of an integrated software component is refered to as its \textit{\ac{API}}. Consumers of an \ac{API} simplify their development effort by taking advantage of the functionality provided without having to worry about its internal implementation, so that they can focus on their own requirements. 

With increasing popularity of distributed systems and the web, APIs have evolved from local libraries to globally available services, providing language-independent access to actions and resources on remote machines which require central coordination or storage.The \ac{W3C} coined the term \textit{Web Service} for services using \textit{\ac{SOAP}} messages that trigger \textit{\acp{RPC}} and are typically transmitted using HTTP with an \acs{XML} serialization\footnote{https://www.w3.org/TR/ws-arch}. Web based services are identified by \textit{\acp{URI}} in either an action-based or resource-based format. Their functionality is described using an \textit{\ac{IDL}} like \textit{\ac{WSDL}} or the OpenAPI Specification. In the remainder of this thesis, \textbf{Web APIs} denote modern, language-agnostic \acp{API}, that are described by \acp{IDL} and can be accessed via HTTP and its standard ports by exchanging non-verbose messages in a human-readable or binary format. We define a verbose format as a messaging format that uses additional elements containing meta information to describe message content instead of implicitly inferring this information by structure or other means. While, contrary to our definition, Web APIs may be provided on ports other than the standard HTTP ports 80 \& 443, this configuration is predominantly found in productive systems.

 According to ProgrammableWeb\footnote{https://www.programmableweb.com/}, one of the world's largest \ac{API} directories, \acs{REST} is the predominant architectural style for Web APIs with over 14,000 \acp{API} listed, followed by \ac{RPC} with about 1,700 entries. Their directory is currently recording an average monthly increase of 168 entries. With new technologies like GraphQL and gRPC emerging, this number will continue to rise. In addition to the consumers, the providers also benefit from supplying an \ac{API}. They are able to increase their customer reach and create a new revenue stream by monetizing it \cite[p. 243]{koci_classification_2019}. 

Despite their many advantages, using external components has one major drawback regarding their evolution. Software evolution denotes all changes to software systems after the initial release, which can also include architectural changes \cite{eilertsen_exploring_2018}. Eilertsen et. al also note that \ac{API} evolution is closely related to software evolution research and is a fairly new field. Due to the decoupled provision and consumption of APIs, the authors refer to the independent evolution process as co-evolution. 

Since providers can unilaterally introduce changes to API contracts, these can cause build or runtime errors in consuming applications, commonly referred to as breaking changes. The prevalent way for library consumers to handle them, was by not upgrading to the latest version. In contrast to statically linked libraries, web services can neither be rolled back nor can a specific version be used beyond the end of its support. Instead, consumers now have to adapt their applications by manually going through a cumbersome process which is associated with a lot of additional effort. For providers, the upgrading forced on their consumers is no desirable option either, in particular for public providers, who in this case might lose customers to alternative providers \cite[p.3]{lubke_interface_2019}. 


\input{content/1_Introduction/1_Motivation}
\input{content/1_Introduction/2_Objectives}
\input{content/1_Introduction/3_Outline}