\subsubsection{Provide Migration Guide and IDL document}
\label{subsubsec:UseCase:MigGuideIDL}

\vspace{-2mm}
\begin{center}
    \def\arraystretch{1.5}
    \begin{longtable}{ p{0.22\linewidth} p{0.72\linewidth} }
    \hline
        \textit{Source} & Web API provider\\
    \hline
        \textit{Stimulus} & New functionality was added to the Web API or existing behavior was changed. Therefore, a new version of the Web API is released. \\
    \hline
    	\textit{Environment} & \textbf{Preconditions:} The provider introduced breaking changes to the exposed interface or behavior when modifying the Web API.
    	
    	\textbf{Postcondition:} The output needs to be published on a publicly accessible server and its URI has to be provided to Web API consumers.
    	\\
    \hline
    	\textit{Artefact} & Migration guide, IDL document\\
    \hline
    \textit{Response} &
    \vspace{-5.1mm}
    \begin{enumerate}[itemindent=-9pt, leftmargin=14pt, itemsep=0pt, align=left]
    	\item The IDL document must describe the publicly exposed interface and behavior. The Web API provider can either manually create this document or generate it using tools.
    	\item The migration guide must contain the type of IDL used to describe the Web API.
    	\item The migration guide must contain the type of Web API.
    	\item The migration guide must contain both the previous and the current version number according to the semantic versioning principles.
    	\item The migration guide can contain a short textual summary to provide an overview of the changes introduced in the current version.
    	\item The migration guide must contain a list of all breaking changes introduced in the current version. 
    \end{enumerate} \\ [-5mm]
    \hline
    \textit{Response Measure} &
    \vspace{-8.5mm}
    \begin{itemize}[itemindent=-9pt, leftmargin=14pt, itemsep=0pt, align=left]
       	\item Success: The migration guide can be retrieved and parsed by migration tool.
       	\item Success: The IDL document can be retrieved and parsed by migration tool.
        \vspace{-5mm}
    \end{itemize}\\
    \hline
    \end{longtable}
\end{center}